---
title: "Homework 5"
author: Diana Sanchez
output: github_document
---

This is my solution to HW5.

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(p8105.datasets)
```


## Problem 1

```{r}
homicides =
  read.csv(
    "./homicide_data/homicide-data.csv")
```

This data describes over 52,000 criminal homicides over the past decade in 50 of the largest American cities. There are `r ncol(homicides)` variables including city and state the homicide occurred in and whether or not the case ended in arrest. There are `r nrow(homicides)` observations.

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df =
  read.csv(
    "./data/homicide-data.csv") %>%
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"),
    city_state = str_c(city, state, sep = "_")) %>%
  select(city_state, resolved) %>%
  filter(city_state != "Tulsa_AL") 

aggregate_df =
  homicide_df %>%
  group_by(city_state) %>%
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>%
  broom::tidy()

results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x= .x, n= .y)),
    tidy_test = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_test) %>%
  select(city_state, estimate, conf.low, conf.high)

results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate))  +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r}
path_df = tibble(
  list.files("lda_data")
) %>%
  mutate(path = str_c("lda_data/", path),
         data = map(.........))

read_csv(path_df$path[[1]])
```


Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.



## Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0
. Generate 5000 datasets from the model

x∼Normal[μ,σ]

For each dataset, save μ̂
 and the p-value arising from a test of H:μ=0
 using α=0.05
. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}
, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ
 on the x axis. Describe the association between effect size and power.
Make a plot showing the average estimate of μ̂
 on the y axis and the true value of μ
 on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂
 only in samples for which the null was rejected on the y axis and the true value of μ
 on the x axis. Is the sample average of μ̂
 across tests for which the null is rejected approximately equal to the true value of μ
? Why or why not?
